---
title: "prof-demographics"
output: html_document
---
getwd()

save.image(file = "prof.RData")
load("prof.RData")
fairly certain this is the correct csv file--I remember that once we decided which departments not to keep, there were 88 of them. i'm also fairly certain i added this csv file to github
```{r}
data <- read.csv("prof-demographics.csv", na.strings=c("","na","-","N/A","NA"), stringsAsFactors=FALSE)
## View(data)
#clean row 613 because inconsistent ("data for both 2010 and 2011 are 0")
# data <- data[-613, ]
library(dplyr)
library(stringr)
library(stringi)
library(purrr)
```

Grabbing the list of department names
```{r}
deptList <- data$Year %>% str_extract_all("[a-z|A-Z]+") 
deptList <- compact(deptList)
length(deptList)
deptNames <- rep(NA, length(deptList))
for (i in 1:length(deptList)){
  deptNames[i] <- str_c(deptList[[i]][1:length(deptList[[i]])], collapse=' ')
}
length(deptNames)
```
Removing commas and last column
```{r}
data$M <- gsub(",", "", data$M)
data$W <- gsub(",", "", data$W)
data$T <- gsub(",", "", data$T)
data <- data[, -12]
head(data)
```

```{r}
"data[data$Year == "2011", ]
data[610:620, ]
data[614, ]
missingRow <- data.frame("Year" = "2011", "F" = "0", "M" = "1", "AI" = "0", "A" = "0", "B" = "0", "L" = "1", "TW" = "0", "U" = "0", "W" = "0", "T" = "1")

data[1:612, ]
data <- rbind(data[1:612, ], missingRow, data[613:nrow(data), ])
data <- data[-614, ]"""
```

Checking to see that each department has something for each year:
```{r}
for (i in 2010:2018) {
  print(length(which(data$Year == i)))
} ## they all do yay
```

```{r}
ethnicities <- c("americanIndian", "asian", "black", "latino", "twoPlus", "unknown", "white")
years <- c("2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018")
```

American Indian: 
```{r}
americanIndian <- character(77)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$AI) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  americanIndian <- cbind(americanIndian, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}
americanIndian <- americanIndian[1:5, -1]
americanIndian
write.csv(americanIndian, "American_Indian.csv", row.names = FALSE)
```

Asian
```{r}
Asian <- character(77)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$A) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  Asian <- cbind(Asian, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}
Asian <- Asian[1:5, -1]
##Asian <- Asian[, -1]
tail(Asian, 20)
Asian
write.csv(Asian, "Asian.csv", row.names = FALSE)

```

Black
```{r}
Black <- character(77)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$B) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  Black <- cbind(Black, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}
Black <- Black[1:5, -1]
#Black <- Black[, -1]
tail(Black, 20)
Black
write.csv(Black, "Black.csv", row.names = FALSE)
```

Latino
```{r}
Latino <- character(77)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$L) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  Latino <- cbind(Latino, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}
Latino <- Latino[1:5, -1]
##Latino <- Latino[, -1]
tail(Latino, 20)
Latino
write.csv(Latino, "Latino.csv", row.names = FALSE)
```

Two or More
```{r}
twoOrMore <- character(77)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$TW) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  twoOrMore <- cbind(twoOrMore, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}
twoOrMore <- twoOrMore[1:5, -1]
twoOrMore
write.csv(twoOrMore, "Two_Plus.csv", row.names = FALSE)
```

Unknown ## we ended up omitting this category, if i remember correctly?
```{r}
Unknown <- character(111)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$U) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  Unknown <- cbind(Unknown, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}
Unknown <- Unknown[1:5, -1]
Unknown
write.csv(Unknown, "Unknown.csv", row.names = FALSE)
```

White
```{r}
White <- character(77)
for (i in 2010:2018) {
  proportions <- as.numeric(data[which(data$Year == i), ]$W) / as.numeric(data[which(data$Year == i), ]$T)
    for (j in 1:length(proportions)) {
      if (is.nan(proportions[j]) == TRUE) {
        proportions[j] <- 0
      }
    }
  propsAndDepts <- as_data_frame(cbind(proportions, deptNames))
  White <- cbind(White, propsAndDepts %>% arrange(desc(proportions))) ## then from here get the top 5 departments and save it somewhere!!!
}

## lastyr <- as.numeric(data[which(data$Year == 2018), ]$W) / as.numeric(data[which(data$Year == 2018), ]$T)

White <- White[1:5, -1]
##White <- White[, -1]
tail(White, 20)
White
write.csv(White, "White.csv", row.names = FALSE)
```











